---
This is from the lda thesis...this talks about the concept of LDA withrespect to mapping it with document categories and also with the hot and cold topics
```{r}
load("pnas-abstracts-meta-dataframe.RData")
str(abstracts_meta)
#get the major category for the year 2001
categories_2001_major <-abstracts_meta$category[abstracts_meta$year==2001]
#get the minor category for the year 2001
categories_2001_minor <- abstracts_meta$category_minor[abstracts_meta$year==2001]

#create a new dataframe containign only the major and minor categories
categories_2001 <- data.frame(major=categories_2001_major, minor=categories_2001_minor,stringsAsFactors = FALSE)

#adding some abbr
categories_2001$major_abbr <- factor(categories_2001_major)
levels(categories_2001$major_abbr) <- c("(BS)","(PS)","(SS)")

#a new string with the major and minor category
categories_2001$pretty <-paste(categories_2001$minor, categories_2001$major_abbr)

#lets see the distribution of the categories
tt<-table(categories_2001$pretty)
sort(tt,decreasing = TRUE)



```

Finiding the topics which will define the category for the document

```{r}
load("model-lda-gibbs-300topics.RData")
theta <- posterior(model_lda)$topics[abstracts_meta$year == 2001,]
#this is the way of converting the per document topic distribution to per category distribution
#for a category first see all the documents that are falling under that category
#then do the col means for the topics
#then you get a single row identified by the categoryname and values = mean value of the topics for that category documents

theta_mean_by <- by(theta, categories_2001$pretty, colMeans)
theta_mean<-do.call("rbind", theta_mean_by)

#this is to find the theta mean ratiion avlur for wach topic calculated as  which has the maximum ratio of j/sum(all without j)
theta_mean_ratios <- theta_mean
for (ii in 1:nrow(theta_mean)) {
  for (jj in 1:ncol(theta_mean)) {
    theta_mean_ratios[ii,jj] <- theta_mean[ii,jj] / sum(theta_mean[ii,-jj])
  }
 }

#sort the topics based on the ratio. The sort will end up in the index locations and not the actual values
topics_by_ratio <- apply(theta_mean_ratios, 1,function(x) sort(x, decreasing = TRUE, index.return = TRUE)$ix)

#this will retrun the index of the highest ratio topics.The index and the name of the topic is the same
topics_most_diagnostic <- topics_by_ratio[1,]

#
#theta_diagnostic <-theta_mean_ratios[,topics_most_diagnostic]
#colnames(theta_diagnostic) <- topics_most_diagnostic

#these are the unique topics
#unique(colnames(theta_diagnostic))

#unstead we can use this
cc=unique(topics_most_diagnostic)
 
for (i in 1:length(cc)) {
    nn=names(which(topics_most_diagnostic==cc[i]))
  #  print(cc[i])
    print (paste(cc[i],"-",nn))
    #nn
}



 


```

Basically we could find out what topics are related to which category

```{r}

#now find the top 5 words for these topics
terms_most_diagnostic <- get_terms (model_lda ,5)[, topics_most_diagnostic]




```
In the above analysis we got a DxK matrix of theta and then we transformed to categoryxTopics matrix and then finally using the most diagnostic method converted to a mapping of categiry and the most diagnostic topic 

Finding hot and cold topics



```{r}
load("model-lda-gibbs-300topics.RData")
load("pnas-abstracts-meta-dataframe.RData")
years <- levels(factor(abstracts_meta$year))
#number of topics
topics_n <- model_lda@k
#get the theta
theta <- posterior(model_lda)$topics

#this time we want to categorize teh theta by year
theta_mean_by_year_by <- by(theta, abstracts_meta$year, colMeans)
theta_mean_by_year <- do.call("rbind",theta_mean_by_year_by)
colnames(theta_mean_by_year) = paste(1:topics_n)
theta_mean_by_year_ts <- ts(theta_mean_by_year,start = as.integer(years[1]))
theta_mean_by_year_time <- time(theta_mean_by_year)


#considering the value of the topic for each year as x and time as 1,2 ,3...basically increafing number we want to see the line of regression ..that is do we see a positive trend or a negative trend in the use of the topic for the documents
theta_mean_lm <- apply(theta_mean_by_year, 2,function(x) lm(x ~ theta_mean_by_year_time))
theta_mean_lm_coef <- lapply(theta_mean_lm, function(x) coef(summary(x)))
#this will give the p value or the level of significance. We baiscally want to see at p=0.001 or less how is the slope value behaving
theta_mean_lm_coef_pvalue <- sapply(theta_mean_lm_coef,'[',"theta_mean_by_year_time","Pr(>|t|)")
#this will give the value of the slope
theta_mean_lm_coef_slope <- sapply(theta_mean_lm_coef,'[',"theta_mean_by_year_time","Estimate")

#so to get the hot topic we will take the topics whose pvalue is significant <0.0001 and sslope sign is positive
highsignificant<-theta_mean_lm_coef_slope[which(theta_mean_lm_coef_pvalue<0.0001)]

table(highsignificant>0)




```


```{r}
B = matrix(c(2, 4, 3, 1, 5, 7,3,2,3,4,5,6,3,2,3,10,11,4,3,4,5,6,3,1),nrow=4,ncol=6) 
sample_theta_mean_by=by(B,c("a","b","c","a"),colMeans)
#this will add the category
sample_theta_mean=do.call("rbind", sample_theta_mean_by)

sample_theta_mean_ratios <- sample_theta_mean
for (ii in 1:nrow(sample_theta_mean)) {
  for (jj in 1:ncol(sample_theta_mean)) {
    sample_theta_mean_ratios[ii,jj] <- sample_theta_mean[ii,jj] / sum(sample_theta_mean[ii,-jj])
  }
 }

sample_topics_by_ratio <- apply(sample_theta_mean_ratios, 1,function(x) sort(x, decreasing = TRUE, index.return = TRUE)$ix)

#actually the index will match the topic number so in the sorting we are using the indexes
sample_topics_most_diagnostic <- sample_topics_by_ratio[1,]


#this step accoring to me is reducdant ..this is just giveing a categiry*topic matrix whose diagnols will have the highest number
sample_theta_diagnostic <-sample_theta_mean_ratios[,sample_topics_most_diagnostic]

colnames(sample_theta_diagnostic) <- sample_topics_most_diagnostic

#these are the unique topics
unique(colnames(sample_theta_diagnostic))



 cc=unique(topics_most_diagnostic)
 
for (i in 1:length(cc)) {
    nn=names(which(topics_most_diagnostic==cc[i]))
  #  print(cc[i])
    print (paste(cc[i],"-",nn))
    #nn
  }


 
 B = matrix(c(2, 4, 3, 1, 5, 7,3,2,3,4,5,6,3,2,3,10,11,4,3,4,5,6,3,1),nrow=4,ncol=6) 
 years=c("1991","1992","1991","1994")
 sample_theta_mean_by=by(B,years,colMeans)
 
 sample_theta_mean_year=do.call("rbind", sample_theta_mean_by)
 sample_theta_mean_by_year_ts <- ts(sample_theta_mean_year,start = as.integer(years[1]))
sample_theta_mean_by_year_time <- time(sample_theta_mean_year)
theta_mean_lm <- apply(sample_theta_mean_year, 2, function(x) lm(x ~ sample_theta_mean_by_year_time))
 

n = c(2.5,4.0,1.0) 
s = c(1,2,3) 
 df = data.frame(n, s)
 
 lm(n~s,data=df)
 
```